Equivalence Testing and the Second Generation P-Value

### 2018-08-16 sgpv_vs_TOST.Rmd
fixed 1 > -1
incorporated changes from google doc, rewrote discussion.

---
title: "Equivalence Testing and the Second Generation P-Value"
author: "Daniël Lakens & Marie Delacre"
date: "15 august 2018"
output: github_document
---

@@

The second generation *p*-value (SGPV) is a new descriptive statistic that was recently proposed to "improve rigor, reproducibility and transparency across science" (Blume, D'Agostino McGowan, Dupont, & Greevy, (2018). The SGPV is 'the proportion of data-supported hypotheses that are also null hypotheses'. The researcher specify an equivalence range around the null hypothesis that specifies values that are considered practically equivalent to the null-hypothesis. The SGPV is the proportion of the  confidence interval (CI) around the observed effect estimate that falls within this equivalence range. If the CI falls completely inside the equivalence range the SGPV is 1, and if the CI falls completely outside the equivalence range the SGPV is 0.

The SGPV has strong similarities with an already existing approach known as equivalence testing (Lakens, 2017; Rogers, Howard, & Vessey, 1993). In an equivalence test, an equivalence range is based upon a smallest effect size of interest. In the Two One-Sided Tests (TOST) approach to equivalence testing data is tested against the upper and lower bounds of the equivalence range (e.g., a difference of -2 and +2). If both one-sided tests reject the presence of effects more extreme than the equivalence bounds we can act as if there is no meaningful effect. Because two one-sided tests are performed, equivalence can be declared when a 1-2*alpha CI (e.g., when the alpha level is 0.05, a 90% CI)  falls completely within the equivalence range of -2 and +2.

Surprisingly, Blume et al (2018) do not discuss equivalence testing in their article, despite the strong conceptual similarities. Here, we aim to examine the similarities and differences between equivalence testing using the TOST procedure and the SGPV. Our goal is to allow researchers to choose the statistic that best answers the question they are interested in.

@@

In the plot below *p*-values are calculated for the TOST equivalence testing procedure where a true population mean ranging from 140 to 150 is compared to the test value of 145 in a one-sample equivalence test where equivalence bounds are set to difference of -2 and +2 around the test value of 145. In other words, the equivalence range in the test contains all means between 143 and 147. Blume et al (2018) rely on the z-distribution, while to TOST package uses the *t*-distribution (which is more accurate at smaller sample sizes). To make sure the SGPV give basically identical results, sample sizes consist of 1000000 observations (for which the *t*-distribution and z-distribution are basically identical). The population standard deviation is set to 500 to still give some variation in responses. Our conclusions should hold to the same extend for more realistic numbers (e.g., N = 100, SD = 1).

@@

@@

lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 1)
lines(p_tost_list, lwd = 3)
abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
```
*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500.

The SGPV treats the equivalence range as the null-hypothesis, while the TOST procedure treats the values outside of the equivalence range as the null-hypothesis. For ease of comparison we can reverse the SGPV (by calculating 1-SGPV) to make the two tests more comparable. We see that the *p*-value from the TOST procedure and the SGPV follow each other closely. 
```{r 1-sgpv_tost, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
plot(NA, 
     ylim = c(0, 1), 
     xlim = c(0, 1001),
     yaxt = "n",
     xaxt = "n",
     ylab = "SGPV or TOST p-value",
     xlab = "Mean")
axis(1, at = seq(0,1000,100), labels = seq(140,150,1), las = 1)
axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)

lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 1)
lines(p_tost_list, lwd = 3)
abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)

```
```{r, include=FALSE}
m <- 145
mu <- 145
sd <- 500
n <- 1000000
low_eqbound = -2 
high_eqbound = 2 
alpha = 0.05

@@

tost_res2 <- TOSTone.raw(m = m, 
                   mu = mu,
                   sd = sd, 
                   n = n, 
                   low_eqbound = low_eqbound, 
                   high_eqbound = high_eqbound, 
                   alpha = alpha
)
SGPV2 <- TOST_to_SGPV(tost_res = tost_res2)
```
*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500.

When the population mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 1000000 and a standard deviation of 500, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r tost_res1$TOST_t1`, *p* = `r tost_res1$TOST_p1`. Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see Figure 1).

@@

The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in Figure 11 below we plot the p-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations. The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05. As the observed correlation in the sample moves from 1 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV. The pattern is quite similar to that in Figure 2. The p-value for the TOST procedure and 1-SGPV are still identical when *p*-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines). There are two important differences, however. First of all, the SGPV is no longer a straight line, but a curve, due to the asymmetry in the 95% CI. Second, and most importantly, the p-value for the equivalence test and the SGPV do no longer overlap at *p* = 0.5. 
```{r, include=FALSE}
n <- 30
r_pop <- .0
low_eqbound_r <- -.45
high_eqbound_r <- .45
alpha <- .05
step <- 0.001

@@

This example illustrates the difference between a proportion and a probability. There is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range. It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between two different questions the SGPV and a *p*-value are answers to. The conclusion of this in depth look at asymmetric confidence intervals is that, while a SGPV of 1 or 0 can still be interpreted the same way as a *p*-value of 0.025 and 0.975 can be interpreted in n equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values. Although Blume et al (2018, p. 3) state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals. Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis'. When the observed correlation equals an equivalence bound, 50% of the normally distributed data is compatible with the null hypothesis (i.e., falls within the equivalence range), even when the SGPV is larger than 0.5.

@@

Given the strong relationship between SGPV and equivalence testing, a logical question is to ask what the introduction of SGPV adds to the existing statistical approaches, including equivalence tests, and what the relative strengths and weaknesses of either approach are. First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic). It numerically summarizes the information that is visually present in a plot (such as Figure 3) displaying the equivalence range and the 95% CI around the observed effect.

The SGPV is 1 for tests where *p*-values for the TOST procedure differ. For example,  different equivalence tests with *p* = 0.024 and *p* = 0.0001 have a SGPV of 1. Although a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range) intermediate values are not as easy to interpret (e.g., it is unclear how we would interpret a SGPV of 0.56 versus 0.65). Since the SGPV is always directly related to a *p*-value from the TOST procedure, different SGPV can be interpreted in the same manner as different *p*-values. From a Fisherian viewpoint, the lower the *p*-value, the worse the fit of the data with a specific model, and analogously, the lower the SGPV the worse the fit of the data with the equivalence range. From a Neyman-Pearson approach to statistics, only the dichotomous rejection of values outside of the equivalence range (TOST *p* < $\alpha$ or SGPV = 1) allows you to act as if the null-hypothesis is true while controlling our error rate at a known maximum.

One weakness of the SGPV is its reliance on the 'small sample correction', where the SGPV is set to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds. This exception to the normal calculation of the SGPV is introduced to prevent misleading values. Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV, which as Blume et al (2018, p. 7) seems to suggest that 'the data favor alternative hypotheses', even when the data is just extremely inaccurate compared to the width of the equivalence range. Although setting the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 is necessary to prevent misleading results, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see Figure 6).

@@

#Discussion

It seems Blume et al (2018) where not aware of the existence of equivalence tests, and we believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*-values to the statistical toolbox. The novelty lies in its use as a descriptive statistic. The added benefit of calculating the proportion of overlap of a 95% CI with the equivalence range, and using this percentage to describe the data, remains somewhat unclear for practical purposes. Nevertheless, our only goal is to clarify the relationship between a newly proposed statistic and the already existing TOST approach used to test for equivalence, and let researchers make an informed decision about which statistical approach provides the best answer to their question.

@@

Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., & Greevy, R. A. (2018). Second-generation *p*-values: Improved rigor, reproducibility, & transparency in statistical analyses. PLOS ONE, 13(3), e0188299. https://doi.org/10.1371/journal.pone.0188299

@@

@@

>>>>

---
title: "Equivalence Testing and the Second Generation P-Value"
author: "Daniël Lakens & Marie Delacre"
date: "16 august 2018"
output: github_document
---

@@

To test predictions most researchers predominantly rely on null-hypothesis tests. 
This statistical approach can be used to examine whether observed data is sufficiently surprising under the null hypothesis to reject an effect size of zero. 
Null-hypothesis tests have an important limitation, in that this procedure can only reject the hypothesis that there is no effect, while scientists should also be able to provide statistical support for *equivalence*. 
When testing for equivalence researchers aim to examine whether the effect is practically zero, or that there is no meaninful effect. 
By specifying a range around the the null hypothesis of values that are deemed practically equivalent to the absence of an effect (i.e., 0 ± 0.3) the observed data can be compared against an *equivalence range* and researchers can test if a meaningful effect is absent (e.g., Hauk & Anderson, 1985; Kruschke, 2018; Metzler, 1974; Rogers, Howard, & Vessey, 1993; Serlin & Lapsey, 1985; Spiegelhalter, Freedman, & Parmar, 1994; Wellek, 2010; Westlake, 1972).

Second generation p-values (SGPV) were recently proposed to as a descriptive statistic that can loosely be interpreted as ‘the proportion of data-supported hypotheses that are also null hypotheses’ (Blume, D’Agostino McGowan, Dupont, & Greevy, 2018). 
The researcher specifies an equivalence range around a classical simple  null hypothesis of parameter values that are considered practically equivalent to the null hypothesis. 
The SGPV measures the degree to which a set of data-supported parameter values falls within the interval null hypothesis. If the estimation interval falls completely within the equivalence range, the SGPV is 1. 
If it lies beyond the equivalence range, the SGPV is 0. Otherwise the SGPV is a value between 0 and 1 that expresses the overlap of data-supported hypotheses and the equivalence range. 
When calculating the SGPV the set of data-supported parameter values can be represented by a confidence interval (CI) or credible intervals or Likelihood support intervals (SI). 
When a confidence interval is used, the SGPV and equivalence tests such as the Two One-Sided Tests (TOST) procedure (Lakens, 2017; Meyners, 2012; Schuirman, 1987) appear to have close ties. 
Here, we aim to examine the similarities and differences between the TOST procedure and the SGPV.

The TOST procedure also relies on the confidence interval around the effect. 
In the TOST procedure the data is tested against the lower equivalence bound in the first one-sided test, and against the upper equivalence bound in the second one-sided test. 
If both tests allow you to reject an effect as extreme or more extreme than the equivalence bound, you can reject the presence of an effect large enough to be meaningful, and conclude the observed effect is practically equivalent to zero. 
Because one-sided tests are performed, one can also conclude equivalence by checking whether the 1-2*alpha confidence interval (e.g., when the alpha level is 0.05, a 90% CI) falls completely within the equivalence bounds. 
Because both equivalence tests as the SGPV are based on whether and how much a confidence interval overlaps with equivalence bounds, it seems logical to compare the newly proposed SGPV to equivalence tests.

@@

To examine the relation between the TOST p-value and the SGPV we can calculate both statistics across a range of observed effect sizes. In Figure 1 *p*-values are plotted for the TOST procedure and the SGPV. The statistics are calculated for one-sample *t*-tests where the observed mean in the sample ranges from 140 to 150 (on the x-axis), the equivalence range is set to 145 ± 2 (i.e., an equivalence range from 143 to 147), a standard deviation of 2 and a sample size of 100.  Our conclusions about the relationship between TOST *p*-values and SGPV in this article are not dependent upon any specific example.

@@

for(i in seq(140, 150, step)){
  count <- count + 1
  m <- i
  mu <- 145
  sd <- 2
  n <- 30
  low_eqbound = -2 
  high_eqbound = 2 
  alpha = 0.05

@@

lines(sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
lines(p_tost_list, lwd = 3)
#abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
```
*Figure 1*: Comparison of *p*-values from TOST (black line) and SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.

The SGPV treats the equivalence range as the null-hypothesis, while the TOST procedure treats the values outside of the equivalence range as the null-hypothesis. For ease of comparison we can reverse the SGPV (by calculating 1-SGPV) to make the values more easily comparable. We see that the *p*-value from the TOST procedure and the SGPV follow each other closely. 
```{r 1-sgpv_tost, echo=FALSE, dpi=600, fig.width=6, fig.height=5}
plot(NA, 
     ylim = c(0, 1), 
     xlim = c(0, 1001),
     yaxt = "n",
     xaxt = "n",
     ylab = "SGPV or TOST p-value",
     xlab = "Mean")
axis(1, at = seq(0,1000,100), labels = seq(140,150,1), las = 1)
axis(2, at = seq(0,1,0.1), labels = seq(0,1,0.1), las = 1)

lines(1-sgpv_list, type="l", col = "darkgrey", lwd = 3, lty = 3)
lines(p_tost_list, lwd = 3)
#abline(h = c(0.975, 0.5, 0.025), col = "grey", lwd = 1, lty = 3)
```
```{r, include=FALSE}
m <- 145
mu <- 145
sd <- 500
n <- 1000000
low_eqbound = -2 
high_eqbound = 2 
alpha = 0.05

@@

tost_res2 <- TOSTone.raw(m = m, 
                   mu = mu,
                   sd = sd, 
                   n = n, 
                   low_eqbound = low_eqbound, 
                   high_eqbound = high_eqbound, 
                   alpha = alpha
)
SGPV2 <- TOST_to_SGPV(tost_res = tost_res2)
```
*Figure 2*: Comparison of *p*-values from TOST (black line) and 1-SGPV (dotted grey line) across a range of true population means (x-axis) tested against a mean of 145 in a one-sample *t*-test with a sample size of 100 and a standard deviation of 2.

When the observed sample mean is 145 and we are testing against equivalence bounds of 143 and 147 using the TOST procedure for a one-sample *t*-test with a sample size of 100 and a standard deviation of 2, the equivalence test is significant, *t*(`r tost_res1$TOST_df`) = `r tost_res1$TOST_t1`, *p* = `r tost_res1$TOST_p1`. Because the 95% CI falls completely within the equivalence bounds, the SGPV is `r SGPV1` (see Figure 1).

@@

The effect of assymetric confidence intervals is most easily noticable at smaller sample sizes, therefore in Figure 11 below we plot the p-values from equivalence tests and the SGPV (again plotted as 1-SGPV for ease of comparison) for correlations. The sample size is 30 pairs of observations, and the lower and upper equivalence bounds are set to -0.45 and 0.45, with an alpha of 0.05. As the observed correlation in the sample moves from -1 to 0 the *p*-value from the equivalence test becomes smaller, as does 1-SGPV. The pattern is quite similar to that in Figure 2. The p-value for the TOST procedure and 1-SGPV are still identical when *p*-values are 0.975 and 0.025 (indicated by the upper and lower horizontal dotted lines). There are two important differences, however. First of all, the SGPV is no longer a straight line, but a curve, due to the asymmetry in the 95% CI. Second, and most importantly, the p-value for the equivalence test and the SGPV do no longer overlap at *p* = 0.5. 
```{r, include=FALSE}
n <- 30
r_pop <- .0
low_eqbound_r <- -.45
high_eqbound_r <- .45
alpha <- .05
step <- 0.001

@@

This example illustrates the difference between a proportion and a probability. There is always a 50% probability of observing a correlation smaller or larger than the true correlation, but the SGPV for this situation depends on how far away the observed correlation is from 0. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% of the correlations observed in the future will fall in this range. It should be noted that in larger sample sizes the SGPV is closer to 0.5 whenever the observed correlation falls on the equivalence bound, but this extreme example nevertheless clearly illustrates the difference between two different questions the SGPV and a *p*-value are answers to. The conclusion of this in depth look at asymmetric confidence intervals is that, while a SGPV of 1 or 0 can still be interpreted the same way as a *p*-value of 0.025 and 0.975 can be interpreted in n equivalence test, since the SGPV and *p*-value for the TOST procedure are always directly related at these values. Although Blume et al (2018, p. 3) state that "the degree of overlap conveys how compatible the data are with the null premise" this definition of what the SGPV provides does not hold for asymmetric confidence intervals. Although a SGPV of 1 or 0 can be directly interpreted, a SGPV between 0 and 1 is not interpretable as 'compatibility with the null hypothesis'. Indeed, Blume and colleagues write in the supplemental material that "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed. However definitive findings, i.e. a p-value of 0 or 1 are *not* affected by the scale changes."

@@

Given the strong relationship between SGPV and equivalence testing, a logical question is to ask what the introduction of SGPV adds to the existing statistical approaches, including equivalence tests, and what the relative strengths and weaknesses of either approach are. First of all, SGPV is a descriptive statistic (unlike the *p*-value that is calculated for an equivalence test, which is an inferential statistic). It numerically summarizes the information that is visually present in a plot of the equivalence range and the confidence interval around the observed effect (for example, see Figure 3).

One benefit of *p*-values over the SGPV is that the SGPV is 0, 0.5, or 1 for a range of observed effects where *p*-values for the TOST procedure continue to differentiate. For example, different equivalence tests with *p* = 0.024 and *p* = 0.0001 have a SGPV of 1. The SGPV provides on average less information than *p*-values.

A possible weakness of the SGPV is that even though a SGPV of 1 or 0 has a clear interpretation (we can reject effects outside or inside the equivalence range), intermediate values are not as easy to interpret (especially for effects that have asymmetric confidence intervals). This is not too problematic, since the main use of the SGPV (e.g., in all examples provided by Blume and colleagues) is to examine whether the SGPV is 0 or 1, or whether the SGPV is inconclusive. This interpretation of a SGPV as allowing researchers to reject the null, reject the presence of a meaningful effect, or remaining inconclusive is very similar to the Neyman-Pearson interpretation of combining a null-hypothesis test and an equivalence test (Lakens, Isager, & Scheel, 2018), although the latter approach also allows researchers to conclude an effect is significant *and* equivalent (i.e., statistically different from zero, but also too small to be considered meaningful). Thus, *p*-values can be interpreted in continuous matter, which is more difficult for the SGPV, and the SGPV is used to classify results into one of three possible outcome, while equivalence tests classify results into four possible outcomes.

One weakness of the SGPV is its reliance on the 'small sample correction', where the SGPV is set to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 and the CI overlaps with the upper and lower bounds. This exception to the normal calculation of the SGPV is introduced to prevent misleading values. Without this correction it is possible that a confidence interval is extremely wide, and an equivalence range is extremely narrow, which without the correction would lead to a very low value for the SGPV, which as Blume et al (2018, p. 7) seems to suggest that 'the data favor alternative hypotheses', even when the data is just extremely inaccurate compared to the width of the equivalence range. Although setting the SGPV to 0.5 whenever the ratio of the confidence interval width to the equivalence range exceeds 2:1 is necessary to prevent misleading results, it leads to a range of situations where the SGPV is set to 0.5, while the *p*-value from the TOST procedure continues to differentiate (see Figure 6). An important benefit of equivalence tests is that is does not need such a correction to prevent misleasing results.

@@

#Conclusion

We believe that our explanation of the similarities between the TOST procedure and the SGPV provides some useful context to interpret the contribution of second generation *p*-values to the statistical toolbox. The novelty lies in its use as a descriptive statistic. There are strong similarities with *p*-values from the TOST procedure, and in all situations where the statistics yield different results, the behavior of the *p*-value from the TOST procedure is more consistent. We hope this overview of the relationship between the SGPV and equivalence tests will help researchers to make an informed decision about which statistical approach provides the best answer to their question.

@@

Blume, J. D., McGowan, L. D., Dupont, W. D., & Greevy, R. A. (2018). Second-generation p-values: Improved rigor, reproducibility, & transparency in statistical analyses. PLOS ONE, 13(3), e0188299. https://doi.org/10.1371/journal.pone.0188299

Hauck, D. W. W., & Anderson, S. (1984). A new statistical procedure for testing equivalence in two-group comparative bioavailability trials. Journal of Pharmacokinetics and Biopharmaceutics, 12(1), 83–91. https://doi.org/10.1007/BF01063612

Kruschke, J. K. (2018). Rejecting or Accepting Parameter Values in Bayesian Estimation. Advances in Methods and Practices in Psychological Science, 2515245918771304. https://doi.org/10.1177/2515245918771304

@@

Lakens, D., Scheel, A. M., & Isager, P. M. (2018). Equivalence Testing for Psychological Research: A Tutorial. Advances in Methods and Practices in Psychological Science, 2515245918770963. https://doi.org/10.1177/2515245918770963

Meyners, M. (2012). Equivalence tests – A review. Food Quality and Preference, 26(2), 231–245. https://doi.org/10.1016/j.foodqual.2012.05.003

@@

Schuirmann, D. J. (1987). A comparison of the two one-sided tests procedure and the power approach for assessing the equivalence of average bioavailability. Journal of Pharmacokinetics and Biopharmaceutics, 15(6), 657–680.

Serlin, R. C., & Lapsley, D. K. (1985). Rationality in psychological research: The good-enough principle.

Spiegelhalter, D. J., Freedman, L. S., & Parmar, M. K. (1994). Bayesian approaches to randomized trials. Journal of the Royal Statistical Society. Series A (Statistics in Society), 357–416. https://doi.org/10.2307/2983527

Wellek, S. (2010). Testing statistical hypotheses of equivalence and noninferiority (2nd ed). Boca Raton: CRC Press.

Westlake, W. J. (1972). Use of confidence intervals in analysis of comparative bioavailability trials. Journal of Pharmaceutical Sciences, 61(8), 1340–1341.
